Agents and you, a brief summary

### 2015-10-29 agents/summery.tex
decided to add the notes on the possible exam questions.
grammar

\section{APL}
Medhi dastani thought about the agent programming langauge (APL)

\subsection{Agent data structure}
This represents the mental state of a agent. \\
\begin{tabular}{ll}
	Name & Does what \\ \toprule
	Beliefs & Information available to the agent \\
	Goals & Objectives that the agent wants to achieve \\
	Events & Obsevations of (environmental) changes \\
	Capabilities & Actions that the agent can perform \\
	Plans & Procedures to achieve objectives \\
	Reasoning rules & Reason about goal and plans \\
\end{tabular} \\

@@

The transition can be executed if $\kappa$ is an active goal (this valuation
is stored in $\tau_1$ \emph{and} $\beta$ is true according to the believe 
base (this eveluation is stored in $\tau_2$). If all these things are true
then $\pi$ is added to the plan base $\Pi$ \emph{but} it will only be executed
if $\tau_1$ and $\tau_2$ return true.

@@

>>>>

\section{APL}
Medhi dastani taught about the agent programming langauge (APL).
\subsection{Agent data structure}
This represents the mental state of a agent. \\
\begin{tabular}{ll}
	Name & Does what \\ \toprule
	Beliefs & Information available to the agent \\
	Goals & Objectives that the agent wants to achieve \\
	Events & Obsevations of (environmental) changes \\
	Capabilities & Actions that the agent can perform \\
	Plans & Procedures to achieve objectives \\
	Reasoning rules & Reason about goal and plans \\
\end{tabular} \\

@@

The transition can be executed if $\kappa$ is an active goal (this valuation
is stored in $\tau_1$ \emph{and} $\beta$ is true according to the believe 
base (this eveluation is stored in $\tau_2$). If all these things are true
then $\pi$ is added to the plan base $\Pi$ \emph{but} it will only be executed
if $\tau_1$ and $\tau_2$ return true.
\subsection{Exam}
some notes I gathered for possible exam questions:

What happens if $\gamma = pos(2,3)$ and $\sigma = pos(4,5)$, resolve with
state transitions.

@@

\subsection{Exam}
